Machine Learned Models for Estimation of Sleep Quality in Free-Living Accelerometer Data

### 2023-01-28 presentation/index.qmd
create flowchart

@@

::: {.column width="30%"}
::: {.fragment}
**Basic Features**

-   Weekday 
-   Time of Day
-   Placement
-   Temperature
:::
:::

::: {.column width="30%"}
::: {.fragment}
**ACC derived features**^[@skotte_detection_2014]

-   Mean ACC X 
-   Mean ACC Y
-   Mean ACC Z
-   Standard Deviation X
-   Standard Deviation Y
-   Standard Deviation Z
-   Max Standard Deviation
-   Inclination
:::
:::

::: {.column width="40%"}
::: {.fragment}
**Sensor-Independent Features**^[@walch_sleep_2019, @forger_simpler_1999]

-   Clock Proxy Linear
-   Clock Proxy Cosinus
:::
:::

@@

:::aside
:::
---

@@

plot_proxy
```

>>>>

## Exclusion Criteria {transition="fade"}

```{r}
#| fig-align: center
source(here::here("presentation/code/flowchart_eligible_nights.R"))

flow
```

::: aside
1. @hirshkowitz_national_2015
:::

@@

::: {.column width="30%"}

**Basic Features**

-   Weekday 
-   Time of Day
-   Placement
-   Temperature

::: {.column width="30%"}

**ACC derived features**^[@skotte_detection_2014]

-   Mean ACC X 
-   Mean ACC Y
-   Mean ACC Z
-   Standard Deviation X
-   Standard Deviation Y
-   Standard Deviation Z
-   Max Standard Deviation
-   Inclination

::: {.column width="40%"}

**Sensor-Independent Features**^[@walch_sleep_2019, @forger_simpler_1999]

-   Clock Proxy Linear
-   Clock Proxy Cosinus

@@

@@

plot_proxy_cos
```

plot_proxy_lin
```
